ECG Disease Classification Using Graph Convolution Networks

### 2017-11-23 Work_report/Final_presentation/btp_presentation.tex
Adding btp

\title{ECG Disease Classification Using Graph Convolution Networks}
% \subtitle{Using Beamer}
\author{Arka Sadhu}
\institute{IIT Bombay}
\date{\today}

@@

\begin{frame}
  \frametitle{CNN on ECG (contd.)}
  \begin{itemize}
  \item Since data is not so much, each ECG data is pre-processed by taking the samples upto fixed period only (eg. 38000 points are broken into 27 partitions).
  \item On top of each convolution layer, we add a batch normalization. This gives accuracy boost upto 93\%-94\%
  \item State of the Art to the best of my knowledge on the PTB dataset is 96\%.
  \item It is also noted that using more number of channels doesn't lead to increase in the accuracy.
  \end{itemize}
  We would like to do better.
\end{frame}

@@

\begin{frame}
  \frametitle{Graph CNN (Optional)}
  Two main approaches to Graph CNN
  \begin{itemize}
  \item Spectral Approach [ChebNet, NIPS2016]
    \begin{itemize}
    \item Basic Idea : Use graph laplacian and do convolution operation in the spectral domain.
    \end{itemize}
  \item Spatial Approach [MoNet, CVPR2017]
    \begin{itemize}
    \item Basic Idea : Use a local manifold and learn in polar coordinates.
    \end{itemize}
  \end{itemize}
  A limitation of Spectral Approach is that the underlying graph should be fixed, which is fortunately the case for ECG.
\end{frame}

@@

% \subsection{How to extend convolution to graphs?}
% \begin{frame}
%   \frametitle{Extending Convolutional to Graphs}
%   There are two main approaches
%   \begin{itemize}
%   \item <1->Spatial Approach :\\
%     Generalization of CNN in the spatial domain itself.
%     \begin{itemize}
%     \item <1-> Learning Convolutional Neural Networks for Graphs [ICML 2016].% \cite{DBLP:journals/corr/NiepertAK16}
%     \end{itemize}
%   \item <2-> Spectral Approach :\\
%     Using the frequency characterization of CNN and using that to generalize to Graphical domain
%     \begin{itemize}
%     \item <2->Spectral Networks and Deep Locally Connected Networks on Graphs [Bruna et al. ICLR 2014]. % \cite{DBLP:journals/corr/BrunaZSL13} %
%     \item <2->Convolutional Neural Networks on Graphs with Fast Localized Spectral Filtering [Defferrard et al. NIPS 2016] (will be the main focus) % \cite{DBLP:journals/corr/DefferrardBV16}
%     \item <2->Semi-Supervised Classification with Graph Convolutional Networks [Kipf et al. ICLR 2017] % \cite{DBLP:journals/corr/KipfW16}
%     \end{itemize}
%   \end{itemize}
% \end{frame}

>>>>

\title{ECG Disease Classification Using Graph Convolution Networks}
% \subtitle{Using Beamer}
\author[Arka Sadhu]{Arka Sadhu \\ Supervised by Prof. Subhasis Chaudhuri}
\institute{IIT Bombay}
\date{\today}

@@

\begin{frame}
  \frametitle{CNN on ECG (contd.)}
  \begin{itemize}
  \item Since data is not so much, each ECG data is pre-processed by taking the samples upto fixed period only (eg. 38000 points are broken into 27 partitions).
  \item On top of each convolution layer, we add a batch normalization. This gives accuracy boost upto 93\%-94\%
  \item State of the Art to the best of my knowledge on the PTB dataset is 96\% [1]
  \item It is also noted that using more number of channels doesn't lead to increase in the accuracy.
  \end{itemize}
  We would like to do better.
\end{frame}

@@

\begin{frame}
  \frametitle{Graph CNN (Optional)}
  Two main approaches to Graph CNN
  \begin{itemize}
  \item Spectral Approach [ChebNet, NIPS2016][2]
    \begin{itemize}
    \item Basic Idea : Use graph laplacian and do convolution operation in the spectral domain.
    \end{itemize}
  \item Spatial Approach [MoNet, CVPR2017][3]
    \begin{itemize}
    \item Basic Idea : Use a local manifold and learn in polar coordinates.
    \end{itemize}
  \end{itemize}
  A limitation of Spectral Approach is that the underlying graph should be fixed, which is fortunately the case for ECG.
\end{frame}

@@

\begin{frame}
  \frametitle{References}
  \begin{enumerate}
  \item L. N. Sharma, R. K. Tripathy and S. Dandapat, "Multiscale Energy and Eigenspace Approach to Detection and Localization of Myocardial Infarction," IEEE Trans. Biomed. Eng. , vol. 62, no. 7, pp. 1827-1837, Jul. 2015
  \item M. Defferrard, X. Bresson, P. Vandergheynst, Convolutional Neural Networks on Graphs with Fast Localized Spectral Filtering, NIPS 2016 (ChebNet framework)
  \item F. Monti*, D. Boscaini*, J. Masci, E. Rodolà, J. Svoboda, M. M. Bronstein, Geometric deep learning on graphs and manifolds using mixture model CNNs, CVPR 2017 (MoNet framework)
  \end{enumerate}

\end{frame}
% \subsection{How to extend convolution to graphs?}
% \begin{frame}
%   \frametitle{Extending Convolutional to Graphs}
%   There are two main approaches
%   \begin{itemize}
%   \item <1->Spatial Approach :\\
%     Generalization of CNN in the spatial domain itself.
%     \begin{itemize}
%     \item <1-> Learning Convolutional Neural Networks for Graphs [ICML 2016].% \cite{DBLP:journals/corr/NiepertAK16}
%     \end{itemize}
%   \item <2-> Spectral Approach :\\
%     Using the frequency characterization of CNN and using that to generalize to Graphical domain
%     \begin{itemize}
%     \item <2->Spectral Networks and Deep Locally Connected Networks on Graphs [Bruna et al. ICLR 2014]. % \cite{DBLP:journals/corr/BrunaZSL13} %
%     \item <2->Convolutional Neural Networks on Graphs with Fast Localized Spectral Filtering [Defferrard et al. NIPS 2016] (will be the main focus) % \cite{DBLP:journals/corr/DefferrardBV16}
%     \item <2->Semi-Supervised Classification with Graph Convolutional Networks [Kipf et al. ICLR 2017] % \cite{DBLP:journals/corr/KipfW16}
%     \end{itemize}
%   \end{itemize}
% \end{frame}
